Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-07-12 SupportingInformation.Rmd
edit make_table fn

fractxt<-function(fracval,numsurrog=1000){
  ptxt<-''
  if (fracval>.5*numsurrog){                        # ?DCR why 0.5 factor?
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

@@

 atdres[1,2]<-fractxt(data$corlmcoru_frac_K)
 atdres[1,3]<-fractxt(data$corlmcoru_frac_S)
 atdres[2,2]<-fractxt(data$PlmPu_frac_K)
 atdres[2,3]<-fractxt(data$PlmPu_frac_S)
 atdres[3,2]<-fractxt(data$D2umD2l_frac_K)
 atdres[3,3]<-fractxt(data$D2umD2l_frac_S)

>>>>

fractxt<-function(fracval,numsurrog){
  ptxt<-''
  if (fracval>.5*numsurrog){                        # ?DCR why 0.5 factor?
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

@@

 atdres[1,2]<-fractxt(data$corlmcoru_frac_K,numsurrog = data$numsurrog_success_K)
 atdres[1,3]<-fractxt(data$corlmcoru_frac_S,numsurrog = data$numsurrog_success_S)
 atdres[2,2]<-fractxt(data$PlmPu_frac_K,numsurrog = data$numsurrog_success_K)
 atdres[2,3]<-fractxt(data$PlmPu_frac_S,numsurrog = data$numsurrog_success_S)
 atdres[3,2]<-fractxt(data$D2umD2l_frac_K,numsurrog = data$numsurrog_success_K)
 atdres[3,3]<-fractxt(data$D2umD2l_frac_S,numsurrog = data$numsurrog_success_S)
